### 2019-05-16 src/diagrams/ugrade-queue.tex
fix line chart for ugrade queue

\begin{tikzpicture}
    \begin{axis}[xlabel={Waktu (detik)}, ylabel={Jumlah jawaban pada antrian}, xmin=0,xmax=1000, ymin=0, ymax=20, legend pos=north east, ymajorgrids=true, grid style=dashed,]
        \addplot[color=green,] table {data/ugrade-queue-gz5-test1.txt};
        \addlegendentry{Pengujian pertama dengan $\textit{grading size} = 5$}
        \addplot[color=green,] table {data/ugrade-queue-gz5-test2.txt};
        \addlegendentry{Pengujian kedua dengan $\textit{grading size} = 5$}
        \addplot[color=green,] table {data/ugrade-queue-gz5-test3.txt};
        \addlegendentry{Pengujian ketiga dengan $\textit{grading size} = 5$}

        \addplot[color=red,] table {data/ugrade-queue-gz2-test1.txt};
        \addlegendentry{Pengujian pertama dengan $\textit{grading size} = 2$}
        \addplot[color=red,] table {data/ugrade-queue-gz2-test2.txt};
        \addlegendentry{Pengujian kedua dengan $\textit{grading size} = 2$}
        \addplot[color=red,] table {data/ugrade-queue-gz2-test3.txt};
        \addlegendentry{Pengujian ketiga dengan $\textit{grading size} = 2$}

        \addplot[color=blue,] table {data/ugrade-queue-gz1-test1.txt};
        \addlegendentry{Pengujian pertama dengan $\textit{grading size} = 1$}
        \addplot[color=blue,] table {data/ugrade-queue-gz1-test2.txt};
        \addlegendentry{Pengujian kedua dengan $\textit{grading size} = 1$}
        \addplot[color=blue] table {data/ugrade-queue-gz1-test3.txt};
        \addlegendentry{Pengujian ketiga dengan $\textit{grading size} = 1$}
    \end{axis}
\end{tikzpicture}

>>>>

\begin{tikzpicture}
    \begin{groupplot}[group style={group size=1 by 3}, xmin=0,xmax=1000, ymin=0, ymax=20, legend pos=north east, ymajorgrids=true, grid style=dashed, height=0.3\textwidth, width=\textwidth]
        \nextgroupplot
        \addplot[color=green,] table {data/ugrade-queue-gz5-test1.txt}; \label{plots:ugrade-queue-gz5}
        \addplot[color=red,] table {data/ugrade-queue-gz2-test1.txt}; \label{plots:ugrade-queue-gz2}
        \addplot[color=blue,] table {data/ugrade-queue-gz1-test1.txt}; \label{plots:ugrade-queue-gz1}
        \coordinate (top) at (rel axis cs:0,1);% coordinate at top of the first plot

        \nextgroupplot[ylabel={Jumlah jawaban pada antrian}]
        \addplot[color=green,] table {data/ugrade-queue-gz5-test2.txt};
        \addplot[color=red,] table {data/ugrade-queue-gz2-test2.txt};
        \addplot[color=blue,] table {data/ugrade-queue-gz1-test2.txt};

        \nextgroupplot[xlabel={Waktu (detik)}]
        \addplot[color=green,] table {data/ugrade-queue-gz5-test3.txt};
        \addplot[color=red,] table {data/ugrade-queue-gz2-test3.txt};
        \addplot[color=blue] table {data/ugrade-queue-gz1-test3.txt};
        \coordinate (bot) at (rel axis cs:1,0);% coordinate at bottom of the last plot
    \end{groupplot}

    \path (top|-current bounding box.north)--
      coordinate(legendpos)
      (bot|-current bounding box.north);
    \matrix[matrix of nodes,anchor=south,draw,inner sep=0.2em,draw]
        at([yshift=1ex]legendpos) {
            \ref{plots:ugrade-queue-gz5}& $\textit{grading size} = 5$ &[5pt]
            \ref{plots:ugrade-queue-gz2}& $\textit{grading size} = 2$ &[5pt]
            \ref{plots:ugrade-queue-gz1}& $\textit{grading size} = 1$ \\
        };
\end{tikzpicture}
